Lens Modeling in \sw

### 2014-06-03 text/ms.tex
2 column, example model figures one per row
updated plot style
added input plots, made mass distr and arr time plots look similar
finetune plots
tex new plot layout
edits
updated images
editing theory part
temp commit
changed topos imgs
cleanup

\documentclass[usenatbib,onecolumn]{mn2e}

@@

@@

@@

\begin{figure}
\centering
\includegraphics[width=.7\hsize]{fig/lenssky}
\caption{Sky distribution of 423 published lenses considered secure as
  of January 2014 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

@@

\begin{figure}
\centering
\includegraphics[height=.3\vsize]{fig/arriv1}
\includegraphics[height=.3\vsize]{fig/arriv2}
\includegraphics[height=.3\vsize]{fig/arriv3}
\caption{Arrival-time surfaces, with contour levels of equal arrival
  time.  The upper surface is with no lens.  The middle surface is
  when a circular lensing mass (offset from the source) is added; a
  maximum, a minimum and a saddle point can be seen.  The last surface
  is the result of an elongated lensing mass; a maximum, two minima
  and two saddle points can be seen.
}
\label{fig:arriv}
\end{figure}

The geometrical time delay \eqref{eq:Ageom} is not the only one.  The
warping of space by a gravitational field introduces a further time
delay $A_{\rm grav}$.  The arrival time of the light ray, compared to
what it would have been with no lensing, is
\begin{equation} \label{eq:Aarriv}
\hbox{arrival time} = A_{\rm geom} + A_{\rm grav} \,.
\end{equation}
We can also express $A_{\rm grav}$ as an area, with the same implicit
constant factor that makes it a time.  The expression, however, is
more complicated.  We first introduce the notation $\nabla^2 f(x,y)$
to denote
\begin{equation}
 \frac{ f(x+\Delta x, y) + f(x-\Delta x, y) +
        f(x, y+\Delta y) + f(x, y-\Delta y) - 4 f(x,y) }
      {\Delta x \; \Delta y}
\end{equation}
in the limit of $\Delta x,\Delta y$ small.  Then we write the
projected mass density of the lens, which would be in $\rm
kg\,m^{-2}$, in special units (given in the Appendix) such that the
surface density becomes a dimensionless field $\kappa(x,y)$.  Then
\begin{equation} \label{eq:Poisson}
\nabla^2 A_{\rm grav}(x,y) = -2\kappa(x,y) \,.
\end{equation}
Note that $A_{\rm grav}(x,y)$ is not given explicitly in terms of
$\kappa(x,y)$, but as a differential equation that must be solved.
Equations of the type \eqref{eq:Poisson} are, however, well known (as
Poisson's equation in two dimensions), and there are techniques for
solving them.  Incidentally, $\kappa$ has a second meaning, as well as
being a dimensionless form of the projected density: it also
measures how a bundle of light rays is brought together by
gravitational lensing, and is called the {\em convergence}.

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006941_input}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007022_input}} \\
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/006919_input}}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  }
  \label{fig:input-spag}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6941_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6941_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000102p_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6941_mass}
    \includegraphics[width=0.45\textwidth]{fig/006941_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6941_cont}
    \includegraphics[width=0.45\textwidth]{fig/006941_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6941_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006941_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6941_atime}
    \includegraphics[width=0.45\textwidth]{fig/006941_arr_time}
  }
  \caption[result 6941 (ASW000102p)]{Model results for a simple
    simulated lens.  (The label ASW000102p in the lower-left panel is
    the \sw identifier for the sky patch where this sim was placed.)
    The model input is shown in the top panel of
    Figure~\ref{fig:input-spag}.  For details of the individual panels
    here, see section \ref{sec:example_models}.}
  \label{fig:6941}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6975_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6975_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW000195x_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6975_mass}
    \includegraphics[width=0.45\textwidth]{fig/006975_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6975_cont}
    \includegraphics[width=0.45\textwidth]{fig/006975_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6975_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006975_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6975_atime}
    \includegraphics[width=0.45\textwidth]{fig/006975_arr_time}
  }
  \caption[result 6975 (ASW000195x)]{A model for a sim with some mass
    substructure. (See Section \ref{sec:example_models} for details.)}
  \label{fig:6975}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6937_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6937_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000vqg_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6937_mass}
    \includegraphics[width=0.45\textwidth]{fig/006937_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6937_cont}
    \includegraphics[width=0.45\textwidth]{fig/006937_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6937_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006937_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6937_atime}
    \includegraphics[width=0.45\textwidth]{fig/006937_arr_time}
  }
  \caption[result 6937 (ASW0000vqg)]{A sim with substructure,
    resulting in a poor mass model. (See Section
    \ref{sec:example_models} for details.)}
  \label{fig:6937}
\end{figure}

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6990_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6990_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0004oux_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6990_mass}
    \includegraphics[width=0.45\textwidth]{fig/006990_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6990_cont}
    \includegraphics[width=0.45\textwidth]{fig/006990_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6990_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006990_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6990_atime}
    \includegraphics[width=0.45\textwidth]{fig/006990_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6915_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6915_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0001hpf_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6915_mass}
    \includegraphics[width=0.45\textwidth]{fig/006915_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6915_cont}
    \includegraphics[width=0.45\textwidth]{fig/006915_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6915_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006915_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6915_atime}
    \includegraphics[width=0.45\textwidth]{fig/006915_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7022_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7022_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:7022_mass}
    \includegraphics[width=0.45\textwidth]{fig/007022_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7022_cont}
    \includegraphics[width=0.45\textwidth]{fig/007022_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7022_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007022_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:7022_atime}
    \includegraphics[width=0.45\textwidth]{fig/007022_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:7025_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:7025_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0000h2m_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:7025_mass}
    \includegraphics[width=0.45\textwidth]{fig/007025_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:7025_cont}
    \includegraphics[width=0.45\textwidth]{fig/007025_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:7025_kappa}
    \includegraphics[width=0.45\textwidth]{fig/007025_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:7025_atime}
    \includegraphics[width=0.45\textwidth]{fig/007025_arr_time}
  }

@@

\begin{figure}
  \centering
  \subfigure[real mass distribution]{
    \label{fig:6919_sim_mass}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_kappa}
  }
  \subfigure[real arrival-time surface]{
    \label{fig:6919_sim_arr}
    \includegraphics[width=0.45\textwidth]{fig/ASW0002z6f_arriv}
  }
  \subfigure[model mass distribution]{
    \label{fig:6919_mass}
    \includegraphics[width=0.45\textwidth]{fig/006919_mass}
  }
  \subfigure[model arrival-time surface]{
    \label{fig:6919_cont}
    \includegraphics[width=0.45\textwidth]{fig/006919_spaghetti}
  }
  \subfigure[real vs model enclosed mass]{
    \label{fig:6919_kappa}
    \includegraphics[width=0.45\textwidth]{fig/006919_kappa_encl}
  }
  \subfigure[model lensed image]{
    \label{fig:6919_atime}
    \includegraphics[width=0.45\textwidth]{fig/006919_arr_time}
  }
  \caption[result 6919 (ASW0002z6f)]{A sim on the border case of
    double vs quad; modelled as a quad.  The model input appears in
    the bottom panel of Figure \ref{fig:input-spag}. (See Section
    \ref{sec:example_models} for details.)}
  \label{fig:6919}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/eR_4}
  \caption{Relative \ERf / \ERg[, sim] for models by volunteers (blue cross), models made by an expert (red cross with offset), including rejected models (green squares); binned per sim.}
  \label{fig:ER_per_sim}
\end{figure}

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007020_kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007024_kappa_encl}}
  \subfigure{\includegraphics[width=0.45\textwidth]
             {fig/007021_kappa_encl}} \\
  \caption{Enclosed mass \kenc from three models of a system with incorrect image identifications. \figref{7022} shows a model (by an expert) with the correct identifications, while \figref{7025} shows a model with error E06 (parities rotated by $\pi/2$).  Shown here are the \kenc results for two models with error E06 and one model (bottom) with error E05 (parities rotated by $\pi$).}
\label{fig:kapenc_compare_faulty}
\end{figure}

@@

\section{More on Lensing Theory} \label{sec:more-theory}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.80\textwidth]{fig/eR_1}
  \caption{\ERf for all models with estimated errors in blue squares, \ERg of simulation in red crosses}
  \label{fig:ER_all_models}
\end{figure}

>>>>

% \documentclass[usenatbib,onecolumn]{mn2e}
\documentclass[usenatbib]{mn2e}

@@

%more abbrevs
\newcommand{\tgeom}{t_{\rm geom}}
\newcommand{\tgrav}{t_{\rm grav}}

@@

\newlength{\myplotswidth}
\setlength{\myplotswidth}{0.4\linewidth}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\hsize]{fig/lenssky}
\caption{Sky distribution of 423 published lenses considered secure as
  of January 2014 (from the Masterlens catalog at the University of
  Utah, maintained by Joel Brownstein and Leonidas Moustakas.) The map
  is in Hammer-Aitoff projection, with North up and $\rm RA=0$ in the
  middle.  The empty swathes to the left and right of center are the
  Milky Way.}
\label{fig:masterlens}
\end{figure}

@@

\begin{equation} \label{eq:tgeom}
\tgeom(x,y) \propto x^2 + y^2 \,.
\end{equation}

\begin{equation} \label{eq:tgrav}
\tgrav = \langle \tgrav^{\textstyle\circ} \rangle
         + (1+z_L) \frac{2G}{c^3} M_{\textstyle\bullet}
\end{equation}

\begin{equation} \label{eq:kappa}
\kappa(x,y) \propto \Sigma(x,y) \,.
\end{equation}

Incidentally, $\kappa$ has a second meaning, as well as
being a dimensionless form of the projected density: it also
measures how a bundle of light rays is brought together by
gravitational lensing, and is called the {\em convergence}.

@@

\begin{figure}
\centering
%\includegraphics[height=.3\vsize]{fig/arriv_0}
%\includegraphics[height=.3\vsize]{fig/arriv_1}
%\includegraphics[height=.3\vsize]{fig/arriv_2}
\includegraphics[width=\columnwidth]{fig/arriv_0}
\includegraphics[width=\columnwidth]{fig/arriv_1}
\includegraphics[width=\columnwidth]{fig/arriv_2}
\caption{Arrival-time surfaces, with contour levels of equal arrival
  time.  The upper surface is with no lens.  The middle surface is
  when a circular lensing mass (offset from the source) is added; a
  maximum, a minimum and a saddle point can be seen.  The last surface
  is the result of an elongated lensing mass; a maximum, two minima
  and two saddle points can be seen.
}
\label{fig:arriv}
\end{figure}

The geometrical time delay \eqref{eq:Ageom} is not the only one.  The
warping of space by a gravitational field introduces a further time
delay $A_{\rm grav}$.  The arrival time of the light ray, compared to
what it would have been with no lensing, is
\begin{equation} \label{eq:Aarriv}
\hbox{arrival time} = t_{\rm geom} + t_{\rm grav} \,.
\end{equation}
We can also express $A_{\rm grav}$ as an area, with the same implicit
constant factor that makes it a time.  The expression, however, is
more complicated.  We first introduce the notation $\nabla^2 f(x,y)$
to denote
\begin{equation}
 \frac{ f(x+\Delta x, y) + f(x-\Delta x, y) +
        f(x, y+\Delta y) + f(x, y-\Delta y) - 4 f(x,y) }
      {\Delta x \; \Delta y}
\end{equation}
in the limit of $\Delta x,\Delta y$ small.  Then we write the
projected mass density of the lens, which would be in $\rm
kg\,m^{-2}$, in special units (given in the Appendix) such that the
surface density becomes a dimensionless field $\kappa(x,y)$.  Then
\begin{equation} \label{eq:Poisson}
\nabla^2 A_{\rm grav}(x,y) = -2\kappa(x,y) \,.
\end{equation}
Note that $A_{\rm grav}(x,y)$ is not given explicitly in terms of
$\kappa(x,y)$, but as a differential equation that must be solved.
Equations of the type \eqref{eq:Poisson} are, however, well known (as
Poisson's equation in two dimensions), and there are techniques for
solving them.

@@

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.9\hsize]
             {fig/006941_input}} \\
  \subfigure{\includegraphics[width=0.9\hsize]
             {fig/007022_input}} \\
  \subfigure{\includegraphics[width=0.9\hsize]
             {fig/006919_input}}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  }
  \label{fig:input-spag}
\end{figure}

@@

% Rafi's original one-coumn design:
%
% \begin{figure}
%   \centering
%   \subfigure[real mass distribution]{
%     \label{fig:6941_sim_mass}
%     \includegraphics[width=0.45\textwidth]{fig/ASW000102p_kappa}
%   }
%   \subfigure[real arrival-time surface]{
%     \label{fig:6941_sim_arr}
%     \includegraphics[width=0.45\textwidth]{fig/ASW000102p_arriv}
%   }
%   \subfigure[model mass distribution]{
%     \label{fig:6941_mass}
%     \includegraphics[width=0.45\textwidth]{fig/006941_mass}
%   }
%   \subfigure[model arrival-time surface]{
%     \label{fig:6941_cont}
%     \includegraphics[width=0.45\textwidth]{fig/006941_spaghetti}
%   }
%   \subfigure[real vs model enclosed mass]{
%     \label{fig:6941_kappa}
%     \includegraphics[width=0.45\textwidth]{fig/006941_kappa_encl}
%   }
%   \subfigure[model lensed image]{
%     \label{fig:6941_atime}
%     \includegraphics[width=0.45\textwidth]{fig/006941_arr_time}
%   }
%   \caption[result 6941 (ASW000102p)]{Model results for a simple
%     simulated lens.  (The label ASW000102p in the lower-left panel is
%     the \sw identifier for the sky patch where this sim was placed.)
%     The model input is shown in the top panel of
%     Figure~\ref{fig:input-spag}.  For details of the individual panels
%     here, see section \ref{sec:example_models}.}
%   \label{fig:6941}
% \end{figure}

% Rafik's two row design
\begin{figure}
  \centering
  \includegraphics[width=\myplotswidth]{fig/006941_input}
  \includegraphics[width=\myplotswidth]{fig/006941_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW000102p_arriv} 
  \includegraphics[width=\myplotswidth]{fig/006941_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW000102p_kappa}
  \includegraphics[width=\myplotswidth]{fig/006941_mass}

  \caption[result 6941 (ASW000102p)]{Model results for a simple
    simulated lens.  (The label ASW000102p in the lower-left panel is
    the \sw identifier for the sky patch where this sim was placed.)
    The model input is shown in the top panel of
    Figure~\ref{fig:input-spag}.  For details of the individual panels
    here, see section \ref{sec:example_models}.}
  \label{fig:6941}
\end{figure}

% Convert all to Phil's scheme:
\begin{figure}
  \includegraphics[width=\myplotswidth]{fig/006975_input}
  \includegraphics[width=\myplotswidth]{fig/006975_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW000195x_arriv.png}
  \includegraphics[width=\myplotswidth]{fig/006975_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW000195x_kappa.png}
  \includegraphics[width=\myplotswidth]{fig/006975_mass}

  \caption[result 6975 (ASW000195x)]{A model for a sim with some mass
    substructure. (See Section \ref{sec:example_models} for details.)}
  \label{fig:6975}
\end{figure}

\begin{figure}
  \centering

  \includegraphics[width=\myplotswidth]{fig/006937_input}
  \includegraphics[width=\myplotswidth]{fig/006937_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0000vqg_arriv}
  \includegraphics[width=\myplotswidth]{fig/006937_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0000vqg_kappa}
  \includegraphics[width=\myplotswidth]{fig/006937_mass}

  \caption[result 6937 (ASW0000vqg)]{A sim with substructure,
    resulting in a poor mass model. (See Section
    \ref{sec:example_models} for details.)}
  \label{fig:6937}
\end{figure}

  %\includegraphics[width=\myplotswidth]{fig/00_input}
  %\includegraphics[width=\myplotswidth]{fig/00_arr_time} \\
  %\includegraphics[width=\myplotswidth]{fig/ASW000_arriv}
  %\includegraphics[width=\myplotswidth]{fig/00_spaghetti} \\
  %\includegraphics[width=\myplotswidth]{fig/ASW000_kappa}
  %\includegraphics[width=\myplotswidth]{fig/00_mass}

\begin{figure}
  \centering

  \includegraphics[width=\myplotswidth]{fig/006990_input}
  \includegraphics[width=\myplotswidth]{fig/006990_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0004oux_arriv}
  \includegraphics[width=\myplotswidth]{fig/006990_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0004oux_kappa}
  \includegraphics[width=\myplotswidth]{fig/006990_mass}

@@

\begin{figure}
  \centering

  \includegraphics[width=\myplotswidth]{fig/006915_input}
  \includegraphics[width=\myplotswidth]{fig/006915_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0001hpf_arriv}
  \includegraphics[width=\myplotswidth]{fig/006915_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0001hpf_kappa}
  \includegraphics[width=\myplotswidth]{fig/006915_mass}

@@

\begin{figure}
  \centering

  \includegraphics[width=\myplotswidth]{fig/007022_input}
  \includegraphics[width=\myplotswidth]{fig/007022_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0000h2m_arriv}
  \includegraphics[width=\myplotswidth]{fig/007022_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0000h2m_kappa}
  \includegraphics[width=\myplotswidth]{fig/007022_mass}

@@

\begin{figure}
  \centering

  \includegraphics[width=\myplotswidth]{fig/007025_input}
  \includegraphics[width=\myplotswidth]{fig/007025_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0000h2m_arriv}
  \includegraphics[width=\myplotswidth]{fig/007025_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0000h2m_kappa}
  \includegraphics[width=\myplotswidth]{fig/007025_mass}

@@

\begin{figure}
  \centering

  \includegraphics[width=\myplotswidth]{fig/006919_input}
  \includegraphics[width=\myplotswidth]{fig/006919_arr_time} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0002z6f_arriv}
  \includegraphics[width=\myplotswidth]{fig/006919_spaghetti} \\
  \includegraphics[width=\myplotswidth]{fig/ASW0002z6f_kappa}
  \includegraphics[width=\myplotswidth]{fig/006919_mass}

  \caption[result 6919 (ASW0002z6f)]{A sim on the border case of
    double vs quad; modelled as a quad.  The model input appears in
    the bottom panel of Figure \ref{fig:input-spag}. (See Section
    \ref{sec:example_models} for details.)}
  \label{fig:6919}
\end{figure}

@@

\begin{figure*}
  \centering
    \includegraphics[width=0.90\linewidth]{fig/eR_5}
  \caption{Relative \ERf / \ERg[, sim] for models by volunteers (blue cross), models made by an expert (red cross with offset), including rejected models (green squares); binned per sim.}
  \label{fig:ER_per_sim}
\end{figure*}

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.9\linewidth]
             {fig/007020_kappa_encl}}
  \subfigure{\includegraphics[width=0.9\linewidth]
             {fig/007024_kappa_encl}}
  \subfigure{\includegraphics[width=0.9\linewidth]
             {fig/007021_kappa_encl}} \\
  \caption{Enclosed mass \kenc from three models of a system with incorrect image identifications. \figref{7022} shows a model (by an expert) with the correct identifications, while \figref{7025} shows a model with error E06 (parities rotated by $\pi/2$).  Shown here are the \kenc results for two models with error E06 and one model (bottom) with error E05 (parities rotated by $\pi$).}
\label{fig:kapenc_compare_faulty}
\end{figure}

@@

\section{Relation to standard lensing formalism} \label{sec:more-theory}

The presentation of the arrival-time surface in \secref{Fermat}
omitted details, for the sake of a more intuitive explanation.
Specifically, the geometric time delay $t_{\rm geom}$ and the
convergence $\kappa$ were left as proportionalities (equations
\ref{eq:tgeom} and \ref{eq:kappa}), and the gravitational time delay
$t_{\rm grav}$ was given in an implicit form (equation
\ref{eq:tgrav}).  We now fill in the details.

The original formulation of the arrival-time surface appears in
equations (2.1) to (2.6) of \cite{1986ApJ...310..568B}.  Their
equations can be rearranged as follows.
\begin{equation} \label{cfBN86}
\begin{aligned}
t_{\rm geom} &= \frac{(1+z_L)}{2c} \frac{d_S}{d_L d_{LS}}
\left[ (x-s_x)^2 + (y-s_y)^2 \right] \\
\nabla^2 t_{\rm grav} &= -(1+z_L)\frac{8\pi G}{c^3} \, \Sigma(x,y) \\
\kappa(x,y) &= \frac{4\pi G}{c^2} \frac{d_L d_{LS}}{d_S}
               \times \Sigma(x,y)
\end{aligned}
\end{equation}
We symbols $d_L,d_S$ and $d_{LS}$ are angular-diameter distances,
respectively from observer to lens, observer to source, and lens to
source.  In the concordance cosmology, we have
\begin{equation}
d_{LS} = \frac{c}{H_0}\,\frac1{1+z_S} \,
\int_{z_L}^{z_S} \!\! \frac{dz}{\sqrt{\Omega_m(1+z)^3 + \Omega_\Lambda}}
%\raise.5ex\hbox{.}
\end{equation}
and similarly $d_S$ and $d_{LS}$.  We have replaced angular positions
on the sky with positions on the lens plane as
\begin{equation}
(x,y) = d_L (\theta_x,\theta_y) \,.
\end{equation}

The first line of equation \eqref{cfBN86} is $t_{\rm geom}$ from
equation \eqref{eq:tgeom} with the proportionality filled in, and with
the source offset at $(s_x,s_y)$ rather than at the origin.

The last line of equation \eqref{cfBN86} fills in the proportionality
factor in equation \eqref{eq:kappa} for the convergence (or
dimensionless surface density) $\kappa$.

The middle line of equation \eqref{cfBN86}, though very different in
form to the expression \eqref{eq:tgrav} for the gravitational time
delay, is in fact equivalent.  This can be shown by considering a
multipole expansions for the solution of the latter equation.  Another
way to see the equivalence is to write a discrete version of
\eqref{eq:tgrav}.  Introducing a small distance $\Delta$, we write
\begin{equation} \label{eq:relax}
\begin{aligned}
\tgrav(x,y) &=
\frac14 \Big[ \tgrav(x+\Delta,y) + \tgrav(x-\Delta,y) + {}\\
&\kern24pt    \tgrav(x,y+\Delta) + \tgrav(x,y-\Delta) \Big] \\
&+ (1+z_L)\frac{2G}{c^3} \, \pi\Delta^2 \, \Sigma(x,y) \,.
\end{aligned}
\end{equation}
The circular average $\langle \tgrav^{\textstyle\circ} \rangle$ has
been replaced by the average over four neighbouring points, and the
enclosed mass $M_{\textstyle\bullet}$ has been replaced by
$\pi\Delta^2\,\Sigma(x,y)$.  Now let us read equation \eqref{eq:relax}
as an iterative formula for $t_{\rm grav}(x,y)$.  It is then
recognisable as a formula for solving the two-dimensional Poisson
equation from \eqref{cfBN86} by relaxation.

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.90\linewidth]{fig/eR_1}
  \caption{\ERf for all models with estimated errors in blue squares, \ERg of simulation in red crosses}
  \label{fig:ER_all_models}
\end{figure}
